---
title: "Shiny Assignment"
author: "Kevin Naik"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r global-options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

## Introduction 

- The core idea is to explore the weather data of Australia available in R.
- The project test and uses ggplot, leaflet with Shiny.
- Basic concepts of time series graph and correlation is implemented.

## Inputs for users 

- Region in Australia from list
- Factor like rainfall, temperature
- Start Date
- End Date
- Coleration factors 1 and 2

## Output in Tabs

- Maps when region is selected it will change using longitude and latitude. 
- Time series plot with factor and date selected by user.
- Coleration Scatter plot with trend line.

## Example of Station name 

```{r echo = FALSE, results='hide'}
library(leaflet)
library(rattle)
m <- leaflet() %>%
   setView(lng = 151.209900, lat = -33.865143, zoom = 5)  %>% 
   addTiles() %>% 
   addMarkers(lat = locationsAUS$latitude,lng = locationsAUS$longitude,popup = locationsAUS$stnID, label = locationsAUS$name)
```

```{r echo = FALSE}
m
```

## Example of Time Series

```{r echo = FALSE, results='hide'}
library(dplyr)
prep <- weatherAUS %>% 
        filter(weatherAUS$Location == "Albury" & between(weatherAUS$Date, as.Date("2008-12-02"), as.Date("2011-01-01")) & !is.na("MinTemp")) %>% 
        select("Date","MinTemp")
```

```{r echo = FALSE}
plot(prep)
```

## Example of GG Plot
```{r echo = FALSE, results='hide'}
library(dplyr)
library(ggplot2)
test <- weatherAUS %>%
            filter(weatherAUS$Location == "Albury" & 
                       between(weatherAUS$Date, as.Date("2008-12-02"),
                                   as.Date("2011-01-01"))) %>%
            select("MinTemp","MaxTemp")
        test <- data.frame(test)
```

```{r echo = FALSE}
ggplot(test, aes(MinTemp, MaxTemp)) + 
            geom_point(color="#69b3a2",alpha = 0.5 ) +
            geom_smooth(color="red", fill="#be79df", se=TRUE)
```

## Thank you
